Approximation as Differentiation

### 2025-07-03 main/first-order.tex
Minor tweaks.

\noindent from which the universal properties of the product and coproduct easily follow. A category $\cat{C}$
with finite biproducts is called \emph{semi-additive}, and cannot be Cartesian closed without being trivial:
since $X \iso 0 \biprod X$, Cartesian closure would imply $\Hom{\cat{C}}{X}{Y} \iso \Hom{\cat{C}}{0}{X
\Rightarrow Y} \iso 1$, and therefore that all objects are isomorphic.

>>>>

\noindent from which the universal properties of the product and coproduct easily follow. A category $\cat{C}$
with finite biproducts is called \emph{semi-additive}. A semi-additive category cannot be Cartesian closed
without being trivial: since we have $X \iso 0 \biprod X$, Cartesian closure would imply $\Hom{\cat{C}}{X}{Y}
\iso \Hom{\cat{C}}{0}{X \Rightarrow Y} \iso 1$, and therefore in such a category all objects are isomorphic.
